Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}

### 2017-05-30 round-corner/paper/bcss/sequoidal.tex
Updated to final version for publication.

\documentclass[a4paper,UKenglish]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

@@

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{William John Gowers}
\author[2]{James Laird}
\affil[1]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
  \texttt{W.J.Gowers@bath.ac.uk}}
\affil[2]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
  \texttt{jiml@cs.bath.ac.uk}}
\authorrunning{W.\,J. Gowers and J. Laird} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{William John Gowers and James Laird}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator, Exponentials}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{}
\EventNoEds{2}
\EventLongTitle{7th Conference on Algebra and Coalgebra in Computer Science (CALCO 2017)}
\EventShortTitle{CALCO 2017}
\EventAcronym{CALCO}
\EventYear{2017}
\EventDate{June 12--16, 2017}
\EventLocation{Ljubljana, Slovenia}
\EventLogo{}
\SeriesVolume{xx}
\ArticleNo{xx}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Additional packages and macros
\usepackage{IEEEtrantools} % for \IEEEeqnarray
\usepackage{pbox} % for \pbox
\usepackage{cmll} % Linear logic symbols!
\usepackage{wasysym} % For left and rigth moons
\usepackage{mathtools}

%% Graphics %%
\usepackage{tikz}
\usetikzlibrary{cd}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}

%% Get the sqsubsetneqq character from the mathabx package
\DeclareFontFamily{U}{mathb}{\hyphenchar\font45}
\DeclareFontShape{U}{mathb}{m}{n}{
      <5> <6> <7> <8> <9> <10> gen * mathb
      <10.95> mathb10 <12> <14.4> <17.28> <20.74> <24.88> mathb12
      }{}
\DeclareSymbolFont{mathb}{U}{mathb}{m}{n}

\DeclareMathSymbol{\sqsubsetneq}    {3}{mathb}{"88}
\DeclareMathSymbol{\varsqsubsetneq} {3}{mathb}{"8A}
\DeclareMathSymbol{\varsqsubsetneqq}{3}{mathb}{"92}
\DeclareMathSymbol{\sqsubsetneqq}   {3}{mathb}{"90}

%% Theorems %%
\theoremstyle{plain}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{exercise}{Exercise}
\theoremstyle{definition}
\newtheorem{notation}[theorem]{Notation}

%% Other macros
\newcommand*\from{\colon}
\def \inv {^{-1}}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\pr}{pr}
\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#2 ; #1}
\newcommand{\cprd}{\sqcup}
\newcommand{\bigcprd}{\bigsqcup}
\newcommand{\C}{\mathcal C}
\newcommand{\F}{\mathcal F}
\newcommand{\G}{\mathcal G}
\newcommand{\W}{\mathcal W}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\newcommand{\emptyplay}{\epsilon}
\newcommand{\prefix}{\sqsubseteq}
\newcommand{\pprefix}{\sqsubsetneqq}
\newcommand{\ppprefix}{\sqsubset}
\DeclareMathOperator{\assoc}{assoc}
\DeclareMathOperator{\lunit}{lunit}
\DeclareMathOperator{\runit}{runit}
\DeclareMathOperator{\sym}{sym}
\newcommand{\braid}{\sym}
\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
\newcommand{\der}{{\mathtt{der}}}
\newcommand{\mult}{{\mathtt{mult}}}
\DeclareMathOperator{\wk}{wk}
\newcommand{\toisom}{{\xrightarrow{\cong}}}
\newcommand{\passoc}{{\mathtt{passoc}}}
\newcommand{\pcomm}{{\mathtt{pcomm}}}
\newcommand{\run}{{\mathtt{r}}}
\newcommand{\lun}{{\mathtt{l}}}
\newcommand{\fcoal}[1]{{\leftmoon #1 \rightmoon}}
\renewcommand{\subset}{\subseteq}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\s}{\mathfrak{s}}
\newcommand{\dist}{{\mathtt{dist}}}
\newcommand{\dec}{{\mathtt{dec}}}
\renewcommand{\int}{{\mathtt{coh}}}
\renewcommand{\coh}{\int}
\DeclareMathOperator{\CCom}{CCom}
\newcommand{\catname}[1]{{\mathsf{#1}}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Ord}{\catname{Ord}}
\newcommand\oppcat[1]{#1^{\mathrm{op}}}
\newcommand{\bN}{{\mathbb{N}}}
\newcommand{\OK}{{\mathtt{OK}}}
\newcommand{\zero}{{\mathtt{zero}}}
\renewcommand{\succ}{{\mathtt{succ}}}
\newcommand{\Var}{{\mathtt{Var}}}
\renewcommand{\read}{{\mathtt{read}}}
\newcommand{\wwrite}{{\mathtt{write}}}
\newcommand{\Rel}{\catname{Rel}}
\newcommand{\inr}{{\mathsf{inr}}}
\newcommand{\inl}{{\mathsf{inl}}}
\newcommand{{\Na}}{\bN}
\newcommand{{\cell}}{{\mathsf{cell}}}
\newcommand{\fix}{{\mathsf{fix}}}
\newcommand{\eq}{{\mathsf{eq}}}
\newcommand{\co}{{\textrm{\textexclamdown}}}

%%OUR

%% Constant width xrightarrows
\newlength{\arrow}
\settowidth{\arrow}{\scriptsize$1000$}
\newcommand*{\constantwidthxrightarrow}[1]{\xrightarrow{\mathmakebox[\arrow]{#1}}}

%% Landscape pages
\usepackage{everypage}
\usepackage{environ}
\usepackage{pdflscape}
\newcounter{abspage}

\makeatletter
\newcommand{\newSFPage}[1]% #1 = \theabspage
  {\global\expandafter\let\csname SFPage@#1\endcsname\null}

\NewEnviron{SidewaysFigure}{\begin{figure}[p]
\protected@write\@auxout{\let\theabspage=\relax}% delays expansion until shipout
  {\string\newSFPage{\theabspage}}%
\ifdim\textwidth=\textheight
  \rotatebox{90}{\parbox[c][\textwidth][c]{\linewidth}{\BODY}}%
\else
  \rotatebox{90}{\parbox[c][\textwidth][c]{\textheight}{\BODY}}%
\fi
\end{figure}}

\AddEverypageHook{% check if sideways figure on this page
  \ifdim\textwidth=\textheight
    \stepcounter{abspage}% already in landscape
  \else
    \@ifundefined{SFPage@\theabspage}{}{\global\pdfpageattr{/Rotate 0}}%
    \stepcounter{abspage}%
    \@ifundefined{SFPage@\theabspage}{}{\global\pdfpageattr{/Rotate 90}}%
  \fi}
\makeatother

>>>>

\documentclass[a4paper,UKenglish]{article}

\input{../../../common/preamble}

\usepackage{microtype}%if unwanted, comment out or use option "draft"
\usepackage{hyperref}

\usepackage[margin=0.5in]{geometry}

@@

\newcommand{\OK}{{\mathtt{OK}}}
\newcommand{\zero}{{\mathtt{zero}}}
\renewcommand{\succ}{{\mathtt{succ}}}
\renewcommand{\read}{{\mathtt{read}}}
\newcommand{\wwrite}{{\mathtt{write}}}

\title{Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}

\author{William John Gowers and James Laird}
